figures_manuscript

### 2024-10-17 pub_figures/manuscript figures.Rmd
volcanos

# Fig 4: Overlaps
```{r overlap, eval=FALSE}
fig <- "Fig4"

res_list[["pcry"]] %>% names()
#  "pcry_D.vs.WT_D"       "pcry_BL.vs.WT_BL"     "pcry_R.vs.WT_R"      
DEGs <- list(dark = res_list$pcry$pcry_D.vs.WT_D %>% subset(padj < 0.05 & (log2FoldChange > 1 | log2FoldChange < -1 )),
             blue = res_list$pcry$pcry_BL.vs.WT_BL %>% subset(padj < 0.05 & (log2FoldChange > 1 | log2FoldChange < -1 )),
             red =res_list$pcry$pcry_R.vs.WT_R %>% subset(padj < 0.05 & (log2FoldChange > 1 | log2FoldChange < -1 )))
DEGs <- lapply(DEGs,data.frame)

venn.ol <- calculate.overlap(DEGs)
# names_res_MO_XX_padj05_abs05 %>% unique()

summary(names_res_MO_XX_padj05_abs05)

venn.ol %>% lapply(length)

input_list <- list(XX=names_res_MO_XX_padj05_abs05,XY=names_res_MO_XY_padj05_abs05)

plt <- venn.diagram(
    x = input_list,
    inverted=TRUE,
    # total.population = TRUE,
    filename = NULL,
    fontfamily ="Arial",
    lwd = 2,
    lty = 'blank',
    fill = cols2[c(1,2)],
    category.names = paste0(names(input_list),"\n(",lapply(input_list,length),")"),
    cat.col=cols2d[c(1,2)],
    cat.fontface = "bold",
    cat.fontfamily = "arial",
    cat.pos = c(+30,-30),
    cat.dist = c(0.12, 0.12),
    disable.logging = TRUE
)

wrap_elements(plt) + plot_annotation(caption = paste0("Total differentially expressed genes: ",deg_table %>% nrow()))

@@

>>>>

# Fig 4: Overlaps
## Fig 4a: Venns
```{r overlap, eval=FALSE}
fig <- "Fig4"

res_list[["pcry"]] %>% names()
#  "pcry_D.vs.WT_D"       "pcry_BL.vs.WT_BL"     "pcry_R.vs.WT_R"      
DEGs <- list(dark = res_list$pcry$pcry_D.vs.WT_D %>% subset(padj < 0.05 & (log2FoldChange > 1 | log2FoldChange < -1 )),
             blue = res_list$pcry$pcry_BL.vs.WT_BL %>% subset(padj < 0.05 & (log2FoldChange > 1 | log2FoldChange < -1 )),
             red =res_list$pcry$pcry_R.vs.WT_R %>% subset(padj < 0.05 & (log2FoldChange > 1 | log2FoldChange < -1 )))
DEGs <- lapply(DEGs,data.frame)
DEGs_genes <- lapply(DEGs,rownames)

venn.ol <- calculate.overlap(DEGs_genes)
venn.ol %>% lapply(length)

input_list <- DEGs_genes

plt <- venn.diagram(
    x = input_list,
    inverted=TRUE,
    # total.population = TRUE,
    filename = NULL,
    fontfamily ="Arial",
    lwd = 2,
    lty = 'blank',
    fill = group.colors[c(2,4,6)],
    category.names = paste0(names(input_list),"\n(",lapply(input_list,length),")"),
#    cat.col=cols2d[c(1,2)],
    cat.fontface = "bold",
    cat.fontfamily = "arial",
#    cat.pos = c(+30,-30),
#    cat.dist = c(0.12, 0.12),
    disable.logging = TRUE
)

wrap_elements(plt) + plot_annotation(caption = paste0("pCRY"))

@@

## Fig 4b: groups
```{r groups}

res_
DEGs_comb <- bind_cols(DEGs[[1]],DEGs[[2]],DEGs[[3]])

# Fig. 3: Grouping
```{r 3_groups, eval=FALSE, fig.show='hold', fig.width=6, fig.height=4, dpi=300, out.width="50%"}

p_new2 <- ggplot(deg_table, aes(x=XX.log2FC, y=XY.log2FC,color=group, fill=group)) + 
  geom_polygon(data = xyup, aes(x=x,y=y),color=cols2l[2],fill=cols2l[2], alpha=0.2) +
  geom_polygon(data = xydo, aes(x=x,y=y),color=cols2l[2],fill=cols2l[2], alpha=0.8) +
  geom_polygon(data = xxdo, aes(x=x,y=y),color=cols2l[1],fill=cols2l[1], alpha=0.8) +
  geom_polygon(data = xxup, aes(x=x,y=y),color=cols2l[1],fill=cols2l[1], alpha=0.2) +
  annotate("text", x= text$x,y= text$y,label = paste(text$label,text$size,sep="\n"), color=text$color,size=3 , fontface="bold") +
  geom_hline(yintercept = 0, linewidth = 0.1) + 
  geom_vline(xintercept = 0, linewidth = 0.1) +
  geom_point(shape=21) + 
  scale_color_manual(values=alpha(c(cols2d[1],cols2d[1], cols2d[2],cols2d[2],rep(colsp,2),rep(colsap,2)),0.8)) +
  scale_fill_manual(values=alpha(c(cols2d[1],cols2d[1], cols2d[2],cols2d[2],rep(colsp,2),rep(colsap,2)),0.3)) +
#  scale_color_manual(values = text$color) +
  coord_cartesian(xlim=c(-10,10),ylim = c(-10,10)) +
  theme_bw() +
  removeGrid(x=T, y=T)

p_new2 + scale_fill_manual(values=c(cols2d[1],cols2d[1], cols2d[2],cols2d[2],alpha(c(rep(colsp,2),rep(colsap,2)),0.3)))
